Manuscript

### 2022-09-05 Manuscript.Rmd
test knit with office machine

---
title: "Manuscript"
date: "`r format(Sys.time(), '%d %B, %Y')`"
author: 
  - Justin Pomeranz:
      email: jfpomeranz@gmail.com
      institute: cmu
      correspondence: true
  - name: James R. Junker
    institute: [glrc, lumcon]
  - name: Jeff S. Wesner
    institute: usd
institute:
  - cmu: Colorado Mesa University, Grand Junction, CO, USA
  - glrc: Great Lakes Research Center, Michigan Technological University, Houghton, MI USA
  - lumcon: Louisiana Universities Marine Consortium, Chauvin, LA USA
  - usd: Dept. of Biology, University of South Dakota, Vermillion, SD, USA
output:
   pdf_document:
     toc: yes
     keep_tex: true
     pandoc_args:
     - '--lua-filter=scholarly-metadata.lua'
     - '--lua-filter=author-info-blocks.lua'
   word_document:
      reference_docx: working_docx_template.docx
      toc: no
      pandoc_args:
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
header-includes:
  - \usepackage{lineno}
  - \usepackage{amsmath}
  - \usepackage{indentfirst}
  - \linenumbers
  - \newcommand{\beginsupplement}{ \setcounter{table}{0} \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
indent: true
linestretch: 1
bibliography: refs.bib
link-citations: no
link-color: grey
csl: ecology.csl
---

@@

**NOTE** I need to integrate reference manager with R markdown. Any favorites or recommendations?? I generally use Zotero (free), but think I have access to Mendeley through CMU...

**NOTE from Jim** I use Zotero, mainly for free and open-source reasons, but I also can have a standalone program that doesn't require internet access, can backup my reference library on the cloud and sync among multiple computers, can spit out bibtex to connect to markdown, and can have group citation lists if neccessary. I use it with a betterBibtex add on that allows for modifying bibtex keys for calling refs in Rmarkdown.

**NOTE** I re-ran all of these after setting the seed for reproducibility. Figures should be up to date, but the numbers may change slightly i.e., 94.8% might become 95.1%, mean $\pm$ SD values will be different.

@@

For each sample of $M$ and each of the 1000 replicates, we estimated the exponent $\lambda$ using MLE methods modified from the the `sizeSpectra` package (Edwards et al. 2020). In addition, we use two common binning methods to estimate the OLS slope parameter in log-log space. For the first binning method, we created 6 equal logarithmic bins covering the range of body sizes. The count in each bin was normalized by dividing by the bin width. This method has been used by (refs here, I think a lot of Woodward's group uses this...) Throughout the manuscript, the normalized equal logarithmic binning method will be referred to as ELBn. The second method was similar to ELBn, but bins of Log~2~ widths are used. The count in each bin is normalized in the same way. This method has been used by [@pomeranz2019; @mcgarvey2019] and is referred to as the Normalized Abundance Spectrum (NAS). Previous work has investigated the biases in $\lambda$ estimates when using different methods (Edwards et al. (2017)[-@edwards2017], Edwards et al. 2020[-@edwards2020], White et al. 2008[-@white2007]). The focus of the present work is to investigate biases when estimating the relationship or relative change in parameters across an environmental gradient. Hence, we do not discuss the $\lambda$ estimates in the main text, but the results are presented in the Supplmental Information.

@@

>>>>

---
title: "Manuscript"
date: "`r format(Sys.time(), '%d %B, %Y')`"
author: 
  - Justin Pomeranz:
      email: jfpomeranz@gmail.com
      institute: cmu
      correspondence: true
  - name: James R. Junker
    institute: [glrc, lumcon]
  - name: Vojsava Gjoni
    institute: usd
  - name: Jeff S. Wesner
    institute: usd
institute:
  - cmu: Colorado Mesa University, Grand Junction, CO, USA
  - glrc: Great Lakes Research Center, Michigan Technological University, Houghton, MI USA
  - lumcon: Louisiana Universities Marine Consortium, Chauvin, LA USA
  - usd: Dept. of Biology, University of South Dakota, Vermillion, SD, USA
output:
   pdf_document:
     toc: yes
     keep_tex: true
     pandoc_args:
     - '--lua-filter=scholarly-metadata.lua'
     - '--lua-filter=author-info-blocks.lua'
   word_document:
      reference_docx: working_docx_template.docx
      toc: no
      pandoc_args:
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
header-includes:
  - \usepackage{lineno}
  - \usepackage{amsmath}
  - \usepackage{indentfirst}
  - \linenumbers
  - \newcommand{\beginsupplement}{ \setcounter{table}{0} \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
indent: true
linestretch: 1
bibliography: refs.bib
link-citations: no
link-color: grey
csl: ecology.csl
---

@@

**NOTE** I'm still working on integrating with Zotero and importing all the necessary references (thanks Jim for the help and instructions!). Don't worry about the **??** references in the rendered version for now.

**Savina** I'm particularly keen to get your feedback on this. I think you mentioned including some other references and discussion in Jeff's Bayesian model paper. If you think they fit in here please let me know or feel free to include them. Likewise, please include any other comments you have, or if you have any insight into how the interpretation of results from different methods would vary.

@@

For each sample of $M$ and each of the 1000 replicates, we estimated the exponent $\lambda$ using MLE methods modified from the the `sizeSpectra` package (Edwards et al. 2020). In addition, we use two common binning methods to estimate the OLS slope parameter in log-log space. For the first binning method, we created 6 equal logarithmic bins covering the range of body sizes. The count in each bin was normalized by dividing by the bin width. This method has been used by (refs here, I think a lot of Woodward's group uses this...) Throughout the manuscript, the normalized equal logarithmic binning method will be referred to as ELBn. The second method was similar to ELBn, but bins of Log~2~ widths are used. The count in each bin is normalized in the same way. This method has been used by [@pomeranz2019; @mcgarvey2019] and is referred to as the Normalized Abundance Spectrum (NAS). Previous work has investigated the biases in $\lambda$ estimates when using different methods (Edwards et al. (2017)[-@edwards2017], Edwards et al. 2020[-@edwards2020], White et al. 2008[-@white2007]). The focus of the present work is to investigate biases when estimating the relationship or relative change in parameters across an environmental gradient. Hence, we do not discuss the $\lambda$ estimates in the main text, but the results are presented in the Supplemental Information (**NOTE** I'm thinking about dropping this from SI. Might be too much info, and it's already been published on by Edwards. Does this add anything to the story??).

@@

**NOTE** I'm considering dropping the $\lambda$ estimate plots from the manuscript. I think it's too much info, but if it adds to the story I'm happy to leave it in. **END**

### 2022-09-05 Manuscript.tex
re-knit updated manuscript sept 4
test knit with office machine

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{setspace}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Manuscript},
  pdfauthor={Justin Pomeranz1,; James R. Junker2,3; Jeff S. Wesner4},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\usepackage{lineno}
\usepackage{amsmath}
\usepackage{indentfirst}
\linenumbers
\newcommand{\beginsupplement}{ \setcounter{table}{0} \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\title{Manuscript}
\author{Justin Pomeranz\textsuperscript{1,*} \and James R.
Junker\textsuperscript{2,3} \and Jeff S. Wesner\textsuperscript{4}}
\date{04 September, 2022}

@@

\textbf{NOTE} I need to integrate reference manager with R markdown. Any
favorites or recommendations?? I generally use Zotero (free), but think
I have access to Mendeley through CMU\ldots{}

\textbf{NOTE from Jim} I use Zotero, mainly for free and open-source
reasons, but I also can have a standalone program that doesn't require
internet access, can backup my reference library on the cloud and sync
among multiple computers, can spit out bibtex to connect to markdown,
and can have group citation lists if neccessary. I use it with a
betterBibtex add on that allows for modifying bibtex keys for calling
refs in Rmarkdown.

\textbf{NOTE} I re-ran all of these after setting the seed for
reproducibility. Figures should be up to date, but the numbers may
change slightly i.e., 94.8\% might become 95.1\%, mean \(\pm\) SD values
will be different.

@@

For each sample of \(M\) and each of the 1000 replicates, we estimated
the exponent \(\lambda\) using MLE methods modified from the the
\texttt{sizeSpectra} package (Edwards et al.~2020). In addition, we use
two common binning methods to estimate the OLS slope parameter in
log-log space. For the first binning method, we created 6 equal
logarithmic bins covering the range of body sizes. The count in each bin
was normalized by dividing by the bin width. This method has been used
by (refs here, I think a lot of Woodward's group uses this\ldots)
Throughout the manuscript, the normalized equal logarithmic binning
method will be referred to as ELBn. The second method was similar to
ELBn, but bins of Log\textsubscript{2} widths are used. The count in
each bin is normalized in the same way. This method has been used by
(Pomeranz et al. 2019, McGarvey et al. 2019) and is referred to as the
Normalized Abundance Spectrum (NAS). Previous work has investigated the
biases in \(\lambda\) estimates when using different methods (Edwards et
al.~(2017)(2017), Edwards et al.~2020(2020), White et al.~2008(2007)).
The focus of the present work is to investigate biases when estimating
the relationship or relative change in parameters across an
environmental gradient. Hence, we do not discuss the \(\lambda\)
estimates in the main text, but the results are presented in the
Supplmental Information.

@@

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{setspace}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Manuscript},
  pdfauthor={Justin Pomeranz1,; James R. Junker2,3; Vojsava Gjoni4; Jeff S. Wesner4},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\usepackage{lineno}
\usepackage{amsmath}
\usepackage{indentfirst}
\linenumbers
\newcommand{\beginsupplement}{ \setcounter{table}{0} \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\title{Manuscript}
\author{Justin Pomeranz\textsuperscript{1,*} \and James R.
Junker\textsuperscript{2,3} \and Vojsava
Gjoni\textsuperscript{4} \and Jeff S. Wesner\textsuperscript{4}}
\date{05 September, 2022}

@@

\textbf{NOTE} I'm still working on integrating with Zotero and importing
all the necessary references (thanks Jim for the help and
instructions!). Don't worry about the \textbf{??} references in the
rendered version for now.

\textbf{Savina} I'm particularly keen to get your feedback on this. I
think you mentioned including some other references and discussion in
Jeff's Bayesian model paper. If you think they fit in here please let me
know or feel free to include them. Likewise, please include any other
comments you have, or if you have any insight into how the
interpretation of results from different methods would vary.

@@

For each sample of \(M\) and each of the 1000 replicates, we estimated
the exponent \(\lambda\) using MLE methods modified from the the
\texttt{sizeSpectra} package (Edwards et al.~2020). In addition, we use
two common binning methods to estimate the OLS slope parameter in
log-log space. For the first binning method, we created 6 equal
logarithmic bins covering the range of body sizes. The count in each bin
was normalized by dividing by the bin width. This method has been used
by (refs here, I think a lot of Woodward's group uses this\ldots)
Throughout the manuscript, the normalized equal logarithmic binning
method will be referred to as ELBn. The second method was similar to
ELBn, but bins of Log\textsubscript{2} widths are used. The count in
each bin is normalized in the same way. This method has been used by
(Pomeranz et al. 2019, McGarvey et al. 2019) and is referred to as the
Normalized Abundance Spectrum (NAS). Previous work has investigated the
biases in \(\lambda\) estimates when using different methods (Edwards et
al.~(2017)(2017), Edwards et al.~2020(2020), White et al.~2008(2007)).
The focus of the present work is to investigate biases when estimating
the relationship or relative change in parameters across an
environmental gradient. Hence, we do not discuss the \(\lambda\)
estimates in the main text, but the results are presented in the
Supplemental Information (\textbf{NOTE} I'm thinking about dropping this
from SI. Might be too much info, and it's already been published on by
Edwards. Does this add anything to the story??).

@@

\textbf{NOTE} I'm considering dropping the \(\lambda\) estimate plots
from the manuscript. I think it's too much info, but if it adds to the
story I'm happy to leave it in. \textbf{END}
